---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

pkgload::load_all()
```

# obtw

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

Oh, by the way: the goal of this package is to offer a set of lightweight tools to simplify data checks in a pipeline.

This package provides two convenience features for working with data transformation pipelines:

- A stack, for pushing the current result and retrieving it for later use

- A validation framework, for reporting multiple failures in a pipeline


## Installation

You can install the development version of obtw like so:

``` r
pak::pak("krlmlr/obtw")
```

(Follow the [installation instructions](https://pak.r-lib.org/#arrow_down-installation) to install pak.)

## Checking one or multiple conditions

```{r error = TRUE}
library(obtw)

test_df <- data.frame(a = 1:3, b = 2:4, c = 1)

# Success returns the input unchanged:
test_df |> 
  obtw_check_df(a <= 3)

# Failure triggers an error:
test_df |> 
  obtw_check_df(a < 3)

# Multiple failures are collected and reported together:
test_df |> 
  obtw_check_df(a < 3) |> 
  obtw_check_df(b > 0) |> 
  obtw_check_df(b < 4)
```

## Integrate with other pipe-friendly checking packages

```{r error = TRUE}
test_df |> 
  obtw_check_df(a < 3) |> 
  obtw(dm::check_key)(c) |> 
  obtw(ensurer::ensure)(nrow(.) == 4) |> 
  obtw(pointblank::col_is_factor)(b) |> 
  obtw(assertr::verify)(a > 7) |> 
  obtw(assertive::assert_is_of_length)(2)
```

## Perform destructive tests on your data

```{r error = TRUE}
# Push with obtw_push(), continue working on your original data with obtw_pop():
test_df |> 
  obtw_push() |> 
  nrow() |>
  obtw(assertive::assert_all_are_greater_than)(1) |> 
  obtw_pop()

# Report all failing checks:
test_df |> 
  obtw_push() |> 
  nrow() |>
  obtw(assertive::assert_all_are_greater_than)(3) |> 
  obtw(assertive::assert_all_are_less_than)(7) |> 
  obtw(assertive::assert_all_are_even)() |> 
  obtw_pop()

# Combine with obtw_check_df():
test_df |> 
  obtw_push() |> 
  dplyr::summarize(b = mean(b)) |> 
  obtw_check_df(b == 2) |> 
  obtw_pop()
```
